Importance of depth refugia for reef resilience and intervention on the Great Barrier Reef under future climate change

### 2025-10-10 paper/paper_draft.qmd
Incorporate CoralBlox equations to complete ADRIA-CoralBlox section

The area of each coral colony is tracked in CoralBlox by the area of a circumference. A
coral population is then represented by a discretised distribution of **eq** coral
diameters, composed of smaller uniform distributions, each representing the number of corals
within a certain diameter range:

**eq**

where **eq** represents the number of intervals used to discretise **eq**, and **eq** and
**eq** are the diameters of the smallest and biggest coral colonies, in that order. The
coral cover for the entire population is given by:

**eq**

These are uniform distributions that compose **eq**, a coral block characteristed by a
diameter density **eq** (the block's height) and a diameter range **eq** (the base of the
block). Therefore, instead of working with a continuous diameter's distribution, CoralBlox
updates each coral block separately. A mortality event is modelled as a decrease in a coral
block's density, and a growth event as an increase in a coral block's diameter range limits.
Both growth and mortality rates are size class dependent, which means the same growth and
mortality rates are used for blocks within a size class. Figure S14 shows a model's
behaviour under low disturbance and no interventions.

>>>>

The area of each coral colony is tracked in CoralBlox by the area of a circumference. A
coral population is then represented by a discretised distribution of $p(x)$ coral
diameters, composed of smaller uniform distributions, each representing the number of corals
within a certain diameter range:

$$
\rho(x) =
\begin{cases}
\lambda_1, & d_0 < x < d_1 \\
\vdots & \vdots \\
\lambda_N, & d_{N-1} < x < d_N \\
0, & x \notin [d_0, d_N]
\end{cases}
$$

where $N$ represents the number of intervals used to discretise $p(x)$, and $d_0$ and $d_N$
are the diameters of the smallest and biggest coral colonies, in that order. The coral cover
for the entire population is given by:

$$
\begin{aligned}
C &= \int_{d_0}^{d_N} \pi x^2 \rho(x) \, dx \\
  &= \sum_{n=1}^{N} \pi \lambda_n \int_{d_{n-1}}^{d_n} x^2 \, dx \\
  &= \sum_{n=1}^{N} \pi \lambda_n \left( \frac{d_n^3 - d_{n-1}^3}{3} \right)
\end{aligned}
$$

These are uniform distributions that compose $p(x)$, a coral block characteristed by a
diameter density $\lambda_n$ (the block's height) and a diameter range $[d_{n-1},d_n]$ (the
base of the block). Therefore, instead of working with a continuous diameter's distribution,
CoralBlox updates each coral block separately. A mortality event is modelled as a decrease
in a coral block's density, and a growth event as an increase in a coral block's diameter
range limits. Both growth and mortality rates are size class dependent, which means the same
growth and mortality rates are used for blocks within a size class. @sfig-coralblox-example
shows a model's behaviour under low disturbance and no interventions.
